|

### 2023-03-20 paper/00-main.Rmd
lmer fit

---
title: |
  STRAIN: A Continuous-Time Within-Play Statistic for Evaluating Pass Rush in American Football with Tracking Data

@@

authors: 
- name: Quang Nguyen
  thanks: Corresponding author's email
  affiliation: Department of Statistics & Data Science, Carnegie Mellon University
- name: Ronald Yurko
  affiliation: Department of Statistics & Data Science, Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: Department of Mathematics and Statistics, Loyola University Chicago

>>>>

---
title: |
  | Bearing the Strain: Analyzing Pass Rush in American Football with Player Tracking Data

# Deforming the line:
# Straining the line:
# Unleashing the Rush
# straining for the takedown
# straining for success
# straining forward
# straining for pressure
# Unleashing the Strain
# Strain on the Gridiron
# from strain to gain
# Bearing the Strain:
# Straining the trenches:

@@

authors: 
- name: Quang Nguyen
  thanks: Corresponding author's email
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Ronald Yurko
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: |
    | Department of Mathematics and Statistics
    | Loyola University Chicago
